Teaching Debugging Collaboratively---Midway Report

### 2020-05-07 paper/midway.tex
Rounding out the inro

\documentclass[12pt, twocolumn]{article}
\usepackage{cite}

@@

Teaching debugging is particuarly important in

>>>>

\documentclass[12pt, twocolumn]{article}
\usepackage{multicol}
\usepackage{cite}

@@

The use of a debugger is particuarly important in a low-level
programming classe, which is often the first time that students
encounter concepts like assembly instructions and memory addresses.
Debuggers such as GCC offer incredibly powerful tools to step through
and inspect running code.  Sadly, low level debugging tools are often
less than intuitive, and provide little to no means for collaboration.
Powerful tools such as RR exist that enable collaborative ``record and
replay'' debugging\cite{DBLP:journals/corr/OCallahanJFHNP17}, but they
lack tools to visualize address spaces and control flow of programs.
Research shows that visualization of these previously unexplored
spaces aids students taking low-level or systems programming
classes\cite{10.1145/3328778.3366894}.\par

The necessity for accessible, collaborative tools for teaching all
aspects of computer science, not the least debugging, has been
exemplified by the current COVID-19 crisis.
